%
% File          : AVI+INTRO.tex
% Description   : A simple template to be used when writing in LaTeX
% Authors       : Avinash Rajaraman
%
% Last Modified : Fri Dec  1 08:17:28 EST 2000
%
% BDOC PARAM offset=0in,0in

% Page style
\documentclass[11pt, pdftex]{article}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{times}
\usepackage{ifthen}
\usepackage{comment}
\usepackage[margin=1in]{geometry}


\title{Introduction to Me}
\author{Avinash Rajaraman}
\date{01/05/2016}


\begin{document}
\maketitle



I joined the undergraduate program in Electronics and Communication Engineering at the National Institute of Technology, Trichy. It was then I realized that Electronics though interesting, did not speak to me as much as  programing. So in tandem I decided to learn what I had always wanted to, in any way possible. Working with  Unity3d , exposed me to JavaScript. After a few weeks I was able to create my first multi-player game. This was also a remake of the classic game “Pocket tanks”, where two players could control individual tanks to try and defeat the other. This was a major step, in that; it gave me the confidence to take up software development from passion to career.

In the summer of 2014, I was recruited as an intern at Symantec Corporation. In hindsight my time as an intern could not have been any better, as it opened a new aspect of computer programming in the form of mobile application development. I was given the sole responsibility to develop an app for Android systems. It was the perfect stimulus to learning development in android along with the execution rigor of creating an industry grade application. For the role I learnt Java from scratch, and later used it to implement the various features of my application. The internship also exposed me to applying parallel processing and JSON parsing concepts. My app was used to appraise and notify the server maintenance team of the status and control elements of a server in real time. 
This experience with a Cyber-security based firm, piqued my interest.

I have always had this interest in video games. The biggest problem in the video game industry is piracy. The sheer number of pirates who distribute them is huge. There have been huge advances in protection of these games, however 
somehow the pirates identify the vulnerabilities and exploit them. I would like this class to help me find the vulnerabilities and understand them so that I can learn to implement them. I am also interested in the encryption and I hope to implement some of my own with the knowledge gained from this. 


\end{document}

